Arc Blanc: a real time ocean simulation framework

### 2025-01-28 paper.tex
Remove CLRS (Cormen 2001) reference

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Calculate the mask}
The FDM needs the height of the vertices below the body.
This is computed from the mask, composed of the vertices of $Z$ contained in one of the intersection polygons at least.
This is done using the \textbf{Point in Polygon} strategy described in Haines (1994) \cite{hainesPointPolygonStrategies1994} and later in Cormen (2001) \cite{CormenIntroductionAlgorithms2001}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Calculate the mask}
The FDM needs the height of the vertices below the body.
This is computed from the mask, composed of the vertices of $Z$ contained in one of the intersection polygons at least.
This is done using the \textbf{Point in Polygon} strategy described in Haines (1994) \cite{hainesPointPolygonStrategies1994}.
